---
title: "p8105_hw6_jl6648"
output: github_document
author: Jixin Li
date: "2023-11-30"
---

```{r}
library(tidyverse)
library(dplyr)
library(broom)
library(boot)
library(modelr)
```

# problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

## create bootstrap function 
```{r}
set.seed(2)
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

## create 5000 bootstrap samples 
```{r}
boot_strap = weather_df |>  
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    results_beta = map(models, broom::glance),
    results_r2 = map(models, broom::tidy)) |> 
  unnest(results_beta, results_r2) |> 
  dplyr::select(.id, term, estimate, r.squared) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  rename(
    beta_0 = `(Intercept)`,
    beta_1 = tmin,
    beta_2 = prcp) 
```

## identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r.squared
```{r}
# find 95% confidence interval for R-squared
r_squared = boot_strap |>
  select(r.squared) |>
  summarize(
    lower_ci = quantile(r.squared, 0.025),
    upper_ci = quantile(r.squared, 0.975)
  ) 

r_squared
```

##  Plot the distribution ofr.squared
```{r}
# plot distribution of r-squared after bootstrapping
boot_strap |>
  select(r.squared) |>
  ggplot(aes(x = r.squared)) + 
  geom_density() + 
  labs(
    title = "Distribution of R-squared estimates",
    x = "Estimated R Squared",
    y = "Density"
  )
```

The distribution of r.squared is approximately normal and it's slightly right-skewed. It has a peak around 0.92, which means the majority of the bootstrapped samples have an r.squared value around 0.92.

## identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for $log(\widehat{\beta_1}*\widehat{\beta_2})$
```{r}
boot_strap_log = boot_strap |> 
   mutate(log = log(beta_0 * beta_1))

log_cl = boot_strap_log |>
  select(log) |> 
  summarize(
    lower_ci = quantile(log, 0.025),
    upper_ci = quantile(log, 0.975)
  )

log_cl
```

##  Plot the distribution of $log(\widehat{\beta_0}*\widehat{\beta_1})$
```{r}
boot_strap_log |>
  select(log) |>
  ggplot(aes(x = log)) + 
  geom_density() + 
  labs(
    title = "Distribution of log(b0*b1) estimates",
    x = "Estimated log(b0*b1)",
    y = "Density"
  )
```

The distribution of log(b0b1) is normal with a peak of 2.1, which means the majority of the bootstrapped samples have an log(b0b1) value around 2.1
