---
title: "p8105_hw6_jl6648"
output: github_document
author: Jixin Li
date: "2023-11-30"
---

```{r}
library(tidyverse)
library(dplyr)
library(broom)
library(boot)
library(modelr)
```

## Problem 1

In the data cleaning code below we create a `city_state` variable, change `victim_age` to numeric, modifiy victim_race to have categories white and non-white, with white as the reference category, and create a `resolution` variable indicating whether the homicide is solved. Lastly, we filtered out the following cities: Tulsa, AL; Dallas, TX; Phoenix, AZ; and Kansas City, MO; and we retained only the variables `city_state`, `resolution`, `victim_age`, `victim_sex`, and `victim_race`.

```{r q1_data_cleaning}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "NA", "Unknown")) |> 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) |> 
  filter(victim_race %in% c("White", "Black")) |> 
  filter(!(city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"))) |> 
  select(city_state, resolution, victim_age, victim_sex, victim_race)
```

Next we fit a logistic regression model using only data from Baltimore, MD. We model `resolved` as the outcome and `victim_age`, `victim_sex`, and `victim_race` as predictors. We save the output as `baltimore_glm` so that we can apply `broom::tidy` to this object and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims.

```{r q1_glm_baltimore}
baltimore_glm = 
  filter(homicide_df, city_state == "Baltimore, MD") |> 
  glm(resolution ~ victim_age + victim_sex + victim_race, family = binomial(), data = _)

baltimore_glm |> 
  broom::tidy() |> 
  mutate(
    OR = exp(estimate), 
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(OR, OR_CI_lower, OR_CI_upper) |>
  knitr::kable(digits = 3)
```

Below, by incorporating `nest()`, `map()`, and `unnest()` into the preceding Baltimore-specific code, we fit a model for each of the cities, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. We show the first 5 rows of the resulting dataframe of model results.

```{r q1_glm_all_cities}
model_results = 
  homicide_df |> 
  nest(data = -city_state) |> 
  mutate(
    models = map(data, \(df) glm(resolution ~ victim_age + victim_sex + victim_race, 
                             family = binomial(), data = df)),
    tidy_models = map(models, broom::tidy)) |> 
  select(-models, -data) |> 
  unnest(cols = tidy_models) |> 
  mutate(
    OR = exp(estimate), 
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(city_state, OR, OR_CI_lower, OR_CI_upper)

model_results |>
  slice(1:5) |> 
  knitr::kable(digits = 3)
```

Below we generate a plot of the estimated ORs and CIs for each city, ordered by magnitude of the OR from smallest to largest. From this plot we see that most cities have odds ratios that are smaller than 1, suggesting that crimes with male victims have smaller odds of resolution compared to crimes with female victims after adjusting for victim age and race. This disparity is strongest in New yrok. In roughly half of these cities, confidence intervals are narrow and do not contain 1, suggesting a significant difference in resolution rates by sex after adjustment for victim age and race. 

```{r q1_plot}
model_results |> 
  mutate(city_state = fct_reorder(city_state, OR)) |> 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = OR_CI_lower, ymax = OR_CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

## create bootstrap function 
```{r}
set.seed(2)
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

## create 5000 bootstrap samples 
```{r}
boot_strap = weather_df |>  
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    results_beta = map(models, broom::glance),
    results_r2 = map(models, broom::tidy)) |> 
  unnest(results_beta, results_r2) |> 
  dplyr::select(.id, term, estimate, r.squared) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  rename(
    beta_0 = `(Intercept)`,
    beta_1 = tmin,
    beta_2 = prcp) 
```

## identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r.squared
```{r}
# find 95% confidence interval for R-squared
r_squared = boot_strap |>
  select(r.squared) |>
  summarize(
    lower_ci = quantile(r.squared, 0.025),
    upper_ci = quantile(r.squared, 0.975)
  ) 

r_squared
```

##  Plot the distribution ofr.squared
```{r}
# plot distribution of r-squared after bootstrapping
boot_strap |>
  select(r.squared) |>
  ggplot(aes(x = r.squared)) + 
  geom_density() + 
  labs(
    title = "Distribution of R-squared estimates",
    x = "Estimated R Squared",
    y = "Density"
  )
```

The distribution of r.squared is approximately normal and it's slightly left-skewed. It has a peak around 0.92, which means the majority of the bootstrapped samples have an r.squared value around 0.92.

## identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for $log(\widehat{\beta_1}*\widehat{\beta_2})$
```{r}
boot_strap_log = boot_strap |> 
   mutate(log = log(beta_1 * beta_2)) |>
   drop_na()

log_cl = boot_strap_log |>
  select(log) |> 
  summarize(
    lower_ci = quantile(log, 0.025),
    upper_ci = quantile(log, 0.975)
  )

log_cl
```

##  Plot the distribution of $log(\widehat{\beta_1}*\widehat{\beta_2})$
```{r}
boot_strap_log |>
  select(log) |>
  ggplot(aes(x = log)) + 
  geom_density() + 
  labs(
    title = "Distribution of log(b1*b2) estimates",
    x = "Estimated log(b1*b2)",
    y = "Density"
  )
```

The distribution of log(b1b2) is left-skewed  with a peak of -5.5, which means the majority of the bootstrapped samples have an log(b0b1) value around -5.5. 

# problem 3
```{r}
bw_df = 
  read_csv("birthweight.csv")
```

## clean the data for regression analysis 
```{r}
bw =
  bw_df |>
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace)) |>
  janitor::clean_names() |> 
  select(bwt,everything())
```

```{r}
sum(is.na(bw))
```
no missing value in this dataset. 

## fit the model
I fit a MLR with all variables as predictor. According to the meaning of each variable, thay are all related with baby’s birth weight somehow. So, I decided to take all variables as predictor. 
```{r}
model_mlr = lm(bwt ~., data = bw)

model_mlr |>
    broom::tidy() |>
    knitr::kable()
```

## plot of model residuals against fitted values
```{r}
 bw |> 
  add_predictions(model_mlr) |>
  add_residuals(model_mlr) |>
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Residuals vs Fitted Values ", 
    xlab("Fitted Value"),
    ylab("Residuals"))
```

the slope in the plot is nearly to 0, which indicates there is no linear relationship between predictors and residuals.

## Compare your model to two others
```{r}
cv_df = 
  crossv_mc(bw, 100) |>
  mutate(
    train = map(train, as_tibble), 
    test = map(test, as_tibble))
```

## plot all three models
```{r}
cv_df |> 
  mutate(
    my_model  = map(train, ~lm(bwt ~., data = .x)),
    model_2  = map(train, ~lm(bwt ~ gaweeks + blength, data = .x)),
    model_3  = map(train, ~lm(bwt ~ bhead*blength*babysex, data = .x))) |>
  mutate(
    rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
    rmse_2    = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y))) |>
  select(starts_with("rmse")) |>  
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |>
  mutate(model = fct_inorder(model)) |>
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin(aes(fill = model))
```

The plot showed my model has the lowest rmse, model 2 has the highest rmse and the rmse of model 3 is slightly higner than my model. 